Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-19 PAPER.tex
fixed authors out of alphabetical order
Tue Dec 19 13:33:40 EST 2017
Tue Dec 19 14:34:13 EST 2017
jonnie edits until section 2.2

\author{
Carina Cheng\altaffilmark{1},
Aaron R. Parsons\altaffilmark{1,2},
Matthew Kolopanis \altaffilmark{3},
Daniel C. Jacobs\altaffilmark{3}, 
Saul A. Kohn\altaffilmark{4},
Adrian Liu\altaffilmark{1,5}, 
James E. Aguirre\altaffilmark{4},
Zaki S. Ali\altaffilmark{1}, 
Richard F. Bradley\altaffilmark{6,7,8},
Gianni Bernardi\altaffilmark{9,10,11}, 
Chris L. Carilli\altaffilmark{12,13},
David R. DeBoer\altaffilmark{2}, 
Matthew R. Dexter\altaffilmark{2},
Joshua S. Dillon\altaffilmark{1},
Pat Klima\altaffilmark{7},
David H. E. MacMahon\altaffilmark{2},
David F. Moore\altaffilmark{4},
Chuneeta D. Nunhokee\altaffilmark{10},
Jonathan C. Pober\altaffilmark{14}, 
William P. Walbrugh\altaffilmark{9},
Andre Walker\altaffilmark{9}
}

\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley CA}
\altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
\altaffiltext{4}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
\altaffiltext{5}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
\altaffiltext{6}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
\altaffiltext{7}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{8}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{9}{Square Kilometer Array, S. Africa, Cape Town South Africa}
\altaffiltext{10}{Dept. of Physics and Electronics, Rhodes University, South Africa}
\altaffiltext{11}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
\altaffiltext{12}{National Radio Astronomy Obs., Socorro NM}
\altaffiltext{13}{Cavendish Lab., Cambridge UK}
\altaffiltext{14}{Dept. of Physics, Brown University, Providence RI}

@@

One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}); . This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations during this transformative era.

Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
the 21 cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{deboer_et_al2017}).

@@

There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
destroying an EoR signal? How can the source of a detection be properly identified? Many common techniques, such as 
averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.

@@

A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, and \citet{trott_et_al2012}. Before showing 
how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
analysis.

We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has length ($N_{t}, N_{f}$), where 
$N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:

@@

One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix. This type of weighting is attractive for power 
spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on 
a measurement (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}). The covariance matrix $\textbf{C}$, which in our case 
describes covariances between frequency channels, can be estimated in a variety of ways. Given perfect foreground, 
instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data. However, if 
our foreground model is flawed, for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in 
the data.

@@

\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $
\textbf{R} = \hat{\textbf{C}}^{-1}$.

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal. In the two panels, we compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left),and projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing EoR-dominating modes. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

@@

If the covariance is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result. An eigenspectrum ranks the eigenvalues of a matrix from 
highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes. This is usually not the case for a covariance matrix, 
for which a sloped eigenspectrum means that modes are given different weights. The modes with the highest eigenvalues are 
down-weighted the most.

@@

The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. If these weak eigenmodes of $\hat{\textbf{C}}$ 
characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-weighted). This leads to the `overfitting' of noise (or rather `overfitting' of signal), which is signal loss.

Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield minimal 
signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
project out the zeroth eigenmode (i.e. zero out all eigenmodes except the first one), thereby down-weighting the foreground-dominating mode only. Hence, we are not using information from all the weaker eigenmodes which carry the risk of 
describing EoR fluctuations. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

>>>>

\author{
Carina Cheng\altaffilmark{1},
Aaron R. Parsons\altaffilmark{1,2},
Matthew Kolopanis \altaffilmark{3},
Daniel C. Jacobs\altaffilmark{3}, 
Saul A. Kohn\altaffilmark{4},
Adrian Liu\altaffilmark{1,5}, 
James E. Aguirre\altaffilmark{4},
Zaki S. Ali\altaffilmark{1}, 
Gianni Bernardi\altaffilmark{6,7,8}, 
Richard F. Bradley\altaffilmark{9,10,11},
Chris L. Carilli\altaffilmark{12,13},
David R. DeBoer\altaffilmark{2}, 
Matthew R. Dexter\altaffilmark{2},
Joshua S. Dillon\altaffilmark{1},
Pat Klima\altaffilmark{7},
David H. E. MacMahon\altaffilmark{2},
David F. Moore\altaffilmark{4},
Chuneeta D. Nunhokee\altaffilmark{10},
Jonathan C. Pober\altaffilmark{14}, 
William P. Walbrugh\altaffilmark{9},
Andre Walker\altaffilmark{9}
}

\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley CA}
\altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
\altaffiltext{4}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
\altaffiltext{5}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
\altaffiltext{6}{Square Kilometer Array, S. Africa, Cape Town South Africa}
\altaffiltext{7}{Dept. of Physics and Electronics, Rhodes University, South Africa}
\altaffiltext{8}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
\altaffiltext{9}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
\altaffiltext{10}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{11}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{12}{National Radio Astronomy Obs., Socorro NM}
\altaffiltext{13}{Cavendish Lab., Cambridge UK}
\altaffiltext{14}{Dept. of Physics, Brown University, Providence RI}

@@

One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}). This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations during this transformative era.

Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
the 21 cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and is forecasted to be able to make a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{deboer_et_al2017}).

@@

There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
destroying an EoR signal? How can a statistically significant detection of a signal be properly identified? Many common techniques, such as 
averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.

@@

A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, and \citet{trott_et_al2016}. Before showing 
how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
analysis.

We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has dimensions ($N_{t}, N_{f}$), where 
$N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:

@@

One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix. This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement. Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}). In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for the PAPER analysis.

The covariance matrix $\textbf{C}$, which describes covariances between frequency channels, can be estimated in a variety of ways. Given perfect foreground, 
instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data. However, if 
our foreground model is flawed, for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in 
the data.

@@

\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The weighting matrix is therefore $
\textbf{R} = \hat{\textbf{C}}^{-1}$.

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal. In the two panels, we compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues differ from those of the true covariance and this error primarily affects the weaker (EoR-dominated) eigenmodes.
There is no signal loss when using only the first eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

@@

If the covariance is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result. An eigenspectrum ranks the eigenvalues of a matrix from 
highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes. This is usually not the case for a covariance matrix, 
for which a sloped eigenspectrum means that modes are given different weights in OQE power spectrum estimation. The modes with the highest eigenvalues are 
down-weighted the most.

@@

The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. For these modes, the error that results from not computing $\textbf{C}$ accurately (due to a finite data sample), has a larger impact on the `weak' modes than the `strong' modes. In other words, mis-estimating $\textbf{C}$ affects EoR-dominated eigenmodes more than FG-dominated modes, and it is primarily the error associated in down-weighting these `weak' modes that leads to signal loss.

Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield minimal 
signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
project out the first eigenmode (i.e. zero out all eigenmodes of the covariance matrix except the first one), thereby down-weighting the foreground-dominating mode only. Hence, we are not using information from all the weaker eigenmodes which have comparatively larger errors. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.
